---
Title: "Peer-Graded Assignment: "
Author: "TheOnlyEnigma"
Date: "22.09.2017"
Output: html_document
---

# PEER-GRADED ASSIGNMENT: REPRODUCIBLE RESEARCH

## Loading and Processing the Data
 
Prior to downloading, and opening up the activity.csv, the basic packages needed need to be opened and downloaded (if neccessary), using the library command. Furthermore a check of the current working directory is completed, and is changed if the user wishes.
 
```{r, echo = TRUE}
 library(knitr)
 library(ggplot2)
 library(dplyr)
 library(lubridate)
 
 getwd()
 setwd("~/Courses/Reproducible_Research/Assignment/repdata_data_activity/RepData_PeerAssessment1")
 dir()
 
```
 
 Reading the data into RStudios, and transforming said data into a suitable format for initial, and further analysis
 
```{r, echo = TRUE}
 zipfile <- "rep_data_activity.zip"
 fileUrl <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
 
 if(!file.exists("activity.csv")) {
  download.file(fileUrl, destfile=zipFile)
  unzip(zipFile)
  file.remove(zipFile)
}

activity <- read.csv("activity.csv", header = TRUE, sep = ",", colClasses = c("numeric", "character", "integer"))
 
```
 
 Check downloaded data using the head function
 
```{r, echo = TRUE}

head(activity)
summary(activity)
    
```

## What is the Mean Total of Steps Taken per Day?

## What is the Average Daily Activity Pattern?

## Inputing the Missing Valiues

## Are there Difference in Activity Patterns between Weekdays and Weekends?
